---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# altituder

[![Travis build status](https://travis-ci.org/romainfrancois/rap.svg?branch=master)](https://travis-ci.org/markusdumke/altituder)

An R package to get altitude (elevation) data from several APIs.

## Installation

You can install the development version of `altituder` from Github via:

``` r
# install.packages("devtools")
devtools::install_github("markusdumke/altituder")
```

## get_altitude

Currently there is only one function `get_altitude`, which queries altitude data
for given locations. 

```{r}
library(altituder)
get_altitude(.longitude = 11, .latitude = 48)

# Input is a data.frame
get_altitude(.Data = data.frame(longitude = 11, latitude = 48))
```

Which API can be specified via the `.src` argument. Currently supported are:

* `geonames`: Uses the geonames webservice. The number of free requests is limited,
              for a higher rate, register and pass your username to this function.
              Check usage terms at [http://www.geonames.org/export/web-services.html].
* `google`: Uses the Google Elevation API.
            You need to pass your API key. Costs can apply.
            Check usage terms at
            [https://developers.google.com/maps/documentation/elevation/usage-and-billing].
* `openelevation`: Uses free Open-Elevation API.
                   See [https://github.com/Jorl17/open-elevation].
* `racemap`: Uses free Racemap API. Based on mapzen terrain data.
             See [https://github.com/racemap/elevation-service].


```{r}
# Set API key via environment variable
# Warning: Costs may apply!
get_altitude(.longitude = 11, .latitude = 48, 
             .src = "google", .google.api.key = Sys.getenv("GOOGLE_API_KEY"))
```